---
title: "EDS Opps, Orgs & More"
---

```{r}
#| echo: false
#| message: false
library(reactable) # create tables
library(googlesheets4) # read in google sheets
library(htmltools)
library(tidyverse)
```

Ongoing list of Environmental Data Science (EDS) opportunities outside of NCEAS. To contribute to this list, add to the [other-eds-opportunities](https://docs.google.com/spreadsheets/d/1y5_7cpGG1eb56cnMZl9sb-AbfaSCc3hidZjs5L7VZoA/edit?usp=sharing) sheet (*Note:* You may have to request access to edit).

If information in this table is inaccurate or broken, please submit an issue to the GitHub `learning-hub-manual` repository **(add link here AFTER transferring repo from hdolinh to NCEAS Enterprise).**

## EDS Programs, Opportunities, Organizations and More

```{r}
#| echo: false
#| message: false
# read in googlesheet "masters-program"
eds_opps <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1y5_7cpGG1eb56cnMZl9sb-AbfaSCc3hidZjs5L7VZoA/edit?usp=sharing", sheet = "eds-opps") %>% 
  # change type and name to class factors for data list filter in table
  mutate(type = as.factor(type),
         name = as.factor(name))
```

```{r}
#| echo: false
# create table using reactable
reactable::reactable(eds_opps,
                     defaultPageSize = 5,
                     highlight = TRUE,
                     striped = TRUE,
                     filterable = TRUE,
                     columns = list(
                       type = colDef("Type",
                                     minWidth = 115,
                                     # SELECT INPUT FILTER #
                                     filterInput = function(values, name) {
                                       htmltools::tags$select(
                                         # Set to undefined to clear the filter
                                         onchange = sprintf("Reactable.setFilter('type-select',
                                                            '%s', event.target.value ||
                                                            undefined)", name),
                                         # "All" has an empty value to clear the filter, and is the default option
                                         htmltools::tags$option(value = "", "All"),
                                         lapply(unique(sort(values)), htmltools::tags$option),
                                         "aria-label" = sprintf("Filter %s", name),
                                         style = "width: 100%; height: 28px;"
                                       ) # EO tags$select
                                     }
                                     ), # EO colDef type
                       name = colDef("Name",
                                     minWidth = 150),
                       affiliation = colDef("Affiliation",
                                            minWidth = 150),
                       twitter_handle = colDef("Twitter Handle",
                                               minWidth = 170,
                                               # add link
                                               cell = function(twitter_handle, index) {
                                                 url <- eds_opps[[index, "twitter_link"]]
                                                 htmltools::tags$a(href = url,
                                                                   target = "_blank",
                                                                   as.character(twitter_handle))
                                               }
                       ), 
                       twitter_link = colDef(show = FALSE),
                       offering = colDef("Offering",
                                         # add link
                                         cell = function(offering, index) {
                                           url <- eds_opps[[index, "offering_link"]]
                                           htmltools::tags$a(href = url,
                                                             target = "_blank",
                                                             as.character(offering))
                                         }
                                         ),
                       offering_link = colDef(show = FALSE),
                       brief_description = colDef("Description", 
                                                  minWidth = 200)
                     ), # EO columns
                     elementId = c("type-select"),
                     defaultSorted = "name"
                     ) # EO reactable


```

## Column Definitions

EDS opportunities are classified into one of the following types:

::: border
| **Type**        | **Definition**                                                                                                                               |
|------------------------|------------------------------------------------|
| Academia        | eds organization affliated with universities, colleges, research labs                                                                        |
| Government      | eds program, opportunity or organization affiliated with a state or federal government agency                                                |
| Independent     | eds program, opportunity or organization that was independently created by an individual or group that is neither a business or a non-profit |
| Masters Program | eds opportunities with a formal degree program at a college or university                                                                    |
| Non-profit      | eds organization that is mission-driven and a non-business entity                                                                            |
:::

[The additional columns are defined as follows:]{style="display:inline-block; margin-top:1rem; margin-bottom:0rem;"}

::: border
| Column         | Definition                                                                                                         |
|------------------------|------------------------------------------------|
| Name           | name of opportunity, organization or program                                                                       |
| Affiliation    | if applicable, name of parent organization, group, school, etc that the organization or program is affiliated with |
| Offering       | type or name of eds opportunity being offered by the organization or program                                       |
| Description    | a very brief description of the eds opportunity                                                                    |
| Twitter Handle | twitter username                                                                                                   |
:::

[There are columns in the [other-eds-opportunities](https://docs.google.com/spreadsheets/d/1y5_7cpGG1eb56cnMZl9sb-AbfaSCc3hidZjs5L7VZoA/edit?usp=sharing) sheet not listed here because they are not shown in this table, but definitions for those columns can be found in the tab **definitions** in the sheet.]{style="display:inline-block; margin-top:1rem; margin-bottom:0rem;"}
